Title

### 2021-02-17 Papers/02_Sound_Compression/SoundRepresentation.tex
write and read binary to disk implemented
working, generally. still some bugs with some wav files

% Background (What is already known about the subject)
sample based virtual instruments are the de facto standard for the emulation of real instruments. nevertheless little attention is given to the encoding of the samples used in those instruments; in fact, lossless containers like wav or proprietary formats are common, pushing the on disk size of those libraries to sizes exceeding the gigabytes.
% Motivation (Why do we care about the problem and the results?) 
This renders the most realistic digital instruments inacessible in many  but the most high end hardware, controllers, like electronic drumkits and controller keyboards. Even less robust personal computers might encounter problems.
% Problem | Objectives (What problem is the paper trying to solve?) (Scope)
We propose a lossy compression algorithm taylored specifically to highly uniform sounds, as those present in this instruments, due to the nature of the sounds, highly redudant, substantial improvements can be obtained, with minimal quality loss.
The method, being physically informed, also serves as base 
% Methods | Procedure | Approach (What did you actually do to get your results?)

@@

% Conclusions | Implications (What are the larger implications of your findings)

>>>>

% Background (What is already known about the subject)
sample based virtual instruments are the de facto standard for the emulation of real instruments. nevertheless little attention is given to the encoding of the samples used in those instruments; in fact, lossless containers like wav or proprietary formats are common, pushing the on disk size of those libraries to sizes exceeding the gigabytes.
% Motivation (Why do we care about the problem and the results?) 
This renders the most realistic digital instruments inacessible in many  but the most high end hardware, controllers, like electronic drumkits and controller keyboards. Even less robust personal computers might encounter problems.
% Problem | Objectives (What problem is the paper trying to solve?) (Scope)
We propose a lossy compression algorithm tailored specifically to highly uniform sounds, as those present in this instruments, due to the nature of the sounds, highly redudant, substantial improvements can be obtained, with minimal quality loss.

% Methods | Procedure | Approach (What did you actually do to get your results?)

@@

% Conclusions | Implications (What are the larger implications of your findings)
The method, being physically informed, also serves as base 
lends itself well to machine learning, as the sound can be represented by an evolving waveform over time (pseudo-cycles)
